Connectome inferences using partial correlation from imaging calcium signal

### 2014-06-14 article.tex
wording

% Introduce notation + goal in mathematical score
% TODO check convention for y_{ij}
The connectomes is represented by a (un)directed graph $G = (V, E)$ comprising
a set of nodes $V$ and a set of edges $E \subseteq \left\{(i, j) \in V \times
V\right\}$, (un)ordered pair from $V$.
Each node $i \in V$ represents a neuron, and each edge $(i, j) \in E$
represents a direct link from a neuron $i$ to a neuron $j$.
The network inference task is set as follows :
\textit{Given the observations $(x_t \in \mathcal{R}^{|V|})_{t=1}^T $
along $T$ periods of time of the $|V|$ neurons, the goal is to infer the
adjacency matrix $A : a_{i,j} = \mathbb{1}((i, j) \in E)$ of the graph $G$,
where $\mathbb{1}$ is the indicator function.}

@@

Let us denote the fluorescence calcium indicators of all neuron
as a set of random variables $X = \left\{X_1, \ldots, X_{|V|}\right\}$, which follows
a joint probability distribution $p_\mathcal{X}$, and by
$X^{-i,j}$ the set of all variables except $X_i$ and $X_j$.
Two random variables $X_i$ and $X_j$ are said to be conditionally independent
to a (possibly empty) set of random variables $Z$, denoted by $X_i \perp X_j | Z$,
if the joint conditional probability distribution factorizes
$p_{\mathcal{X}_i, \mathcal{X}_j|\mathcal{Z}} = p_{\mathcal{X}_i|\mathcal{Z}}
p_{\mathcal{X}_j|\mathcal{Z}}$.  The inference of the undirected network
can be formulated as inferring conditional dependences
$X_i \not\perp X_j | X^{-i,j}$ between all pair of fluorescence signal
$i$ and $j$, in other words the inferred network will be
$\hat{A}: \hat{a}_{i,j} = \mathbb{1}(X_i \not\perp X_j | X^{-i,j}), \forall i, j \in V$.

>>>>

% Introduce notation + goal in mathematical score
% TODO check convention for y_{ij}
The connectomes, the neural network, is represented by a (un)directed graph $G = (V, E)$ comprising
a set of nodes $V$ and a set of edges $E \subseteq \left\{(i, j) \in V \times
V\right\}$, (un)ordered pair from $V$.
Each node $i \in V$ represents a neuron, and each edge $(i, j) \in E$
represents a direct link from a neuron $i$ to a neuron $j$.
The network inference task is set as follows :
\textit{Given the observations $(x_t \in \mathcal{R}^{|V|})_{t=1}^T $
along $T$ periods of time of the $|V|$ neurons, the goal is to infer the
adjacency matrix $A : a_{i,j} = \mathbb{1}((i, j) \in E)$ of the neural network
of graph $G$, where $\mathbb{1}$ is the indicator function.}

@@

Let us denote the fluorescence calcium indicators of all neuron
as a set of random variables $X = \left\{X_1, \ldots, X_{|V|}\right\}$, which follows
a joint probability distribution $p_\mathcal{X}$, and by
$X^{-i,j}$ the set of all variables except $X_i$ and $X_j$.
Two random variables $X_i$ and $X_j$ are said to be conditionally independent
to a (possibly empty) set of random variables $Z$, denoted by $X_i \perp X_j | Z$,
if the joint conditional probability distribution factorizes
$p_{\mathcal{X}_i, \mathcal{X}_j|\mathcal{Z}} = p_{\mathcal{X}_i|\mathcal{Z}}
p_{\mathcal{X}_j|\mathcal{Z}}$.  The inference of the undirected network
can be formulated as inferring conditional dependences
$X_i \not\perp X_j | X^{-i,j}$ between all pairs $i$ and $j$ of fluorescence
signals, in other words the inferred network will be
$\hat{A}: \hat{a}_{i,j} = \mathbb{1}(X_i \not\perp X_j | X^{-i,j}), \forall i, j \in V$.
